### 2023-05-23 paper/content.tex
Updates from Overleaf

Figure~\ref{non-dipolarity-synthetic-data} shows the synthetic $b_z$ of an example non-dipolar particle at variable source-sample distances.
When the particle is close to the sensor (\qty{1-3}{\um}), the observed field is strongly non-dipolar (Figure~\ref{non-dipolarity-synthetic-data}a-b) and the dipole moment inversion produces low $R^2$ values. 
As the distance increases, the magnetic field is attenuated, particularly the non-dipolar components which decay more rapidly than the dipolar component.
This results in an increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d). 
At distances above \qty{5}{\um}, there is practically only the contribution of the dipolar component, causing $R^2$ to approach its maximum value of 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).

>>>>

Figure~\ref{non-dipolarity-synthetic-data} shows the synthetic $b_z$ of an example non-dipolar particle at variable source-sample distances.
When the particle is close to the sensor (\qtyrange{1}{3}{\um}), the observed field is strongly non-dipolar (Figure~\ref{non-dipolarity-synthetic-data}a-b) and the dipole moment inversion produces low $R^2$ values. 
As the distance increases, the magnetic field is attenuated, particularly the non-dipolar components which decay more rapidly than the dipolar component.
This results in an increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d). 
At distances above \qty{5}{\um}, there is practically only the contribution of the dipolar component, causing $R^2$ to approach its maximum value of 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).
